\thetitle

### 2021-05-24 writing/conclusion.tex
Small fixes from meeting last week

The interviews of~\citet{tgpk-dls-2018} suggests that programmers
prefer the run-time checking of Natural over other soundness methods. But,
the opinion of a random set of programmers does not mean that blame
assignment adds value. Similarly, researchers and language designers have
implicitly answered this question one way or another without evidence for the
blame-strategy dimension. The experiment presented in this paper provides some
justification for the programmers' leanings
\ll{Does it really?} \mf{addressed}
and helps language creators revisit
their decisions. Of course, the design choice remains a trade-off
along several dimensions, and  the presented experiment sheds light on
only one of them.

>>>>

The interviews of~\citet{tgpk-dls-2018} suggests that programmers
prefer the run-time checking of Natural over other soundness methods. But,
the opinion of a random set of programmers does not mean that blame
assignment adds value. Similarly, researchers and language designers have
implicitly answered this question one way or another without evidence for the
blame-strategy dimension. The experiment presented in this paper provides some
justification for the programmers' leanings and helps language creators revisit
their decisions. Of course, the design choice remains a trade-off
along several dimensions, and  the presented experiment sheds light on
only one of them.

### 2021-05-24 writing/results.tex
the rest, minus the revisions of the results and discussion sections
Small fixes from meeting last week

The test bed for executing the experimental process utilizes a machine with two
Intel Xeon Gold 6258R processors (28 doubly-threaded cores each) and 500GB of
memory.  Each debugging scenario had a 4 minute timeout and a 6GB memory
limit. Running the experiment on all debugging scenarios took over
30,000 compute hours.

@@

Figure~\ref{fig:avo-bars} also provides answers for $Q_*$. Blame for all three
semantics is significantly more useful than Erasure exceptions --- by almost
12\% for Natural and almost 9\% for Transient. Natural blame is more useful than
both versions of Transient blame by a small percentage (about 4\%). The
Transient first and Transient last blame are practically indistinguishable.
Finally, Natural exceptions are more useful than Transient exceptions, although
only in a small percentage of scenarios (about 2.5\%). A rare few scenarios
(about 0.5\%) show the opposite, despite the theoretically advantageous
additional checks of Natural.

>>>>

The test bed for executing the experimental process utilizes a machine with two
Intel Xeon Gold 6258R processors (28 doubly-threaded cores each) and 500GB of
memory.  Each debugging scenario had a 4 minute timeout and a 6GB memory
limit. Running the experiment on all debugging scenarios took over
30,000 compute hours or roughly three-and-a-half compute years.

@@

Figure~\ref{fig:avo-bars} also provides answers for $Q_*$. Blame for all three
semantics is significantly more useful than Erasure exceptions---by almost
12\% for Natural and almost 9\% for Transient. Natural blame is more useful than
both versions of Transient blame by a small percentage (about 4\%). The
Transient first and Transient last blame are practically indistinguishable.
Finally, Natural exceptions are more useful than Transient exceptions, although
only in a small percentage of scenarios (about 2.5\%). A rare few scenarios
(about 0.5\%) show the opposite, despite the theoretically advantageous
additional checks of Natural.
